\textls[-0]{\thetitle}

### 2023-04-01 casestudies.tex
say less
seems more appropriate to say RState is a concretization relation?

A second family \lsti{ImpGAI} (\textasciitilde 550~LOC) extends \lsti{Imp}.
It exports a generic framework for deriving
abstract interpreters with partial-correctness guarantees.
Soundness of the abstract interpreter, \lsti{analyze},
is stated with respect to the interpreter, \lsti{eval}, inherited from \lsti{Imp}.
The theorem says that the abstraction relation \lsti{RState} over a
concrete state~\lsti{S} and an abstract state~\lsti{absS} is preserved
by the analysis:

@@

\noindent
\lsti{analyze} is defined via \lsti{FRecursion}, and the soundness theorem
is proved via \lsti{FInduction}.
This family leaves fields representing the abstract domain, the
abstraction relation, monotonicity of transfer functions, etc.\ 
largely unspecified or unproven---a derived family can further bind
these ``parameters'' by overriding appropriate fields (and also possibly
extend the abstract syntax), to create a sound, runnable abstract
interpreter for a (possibly extended) while-language.
%\EDJ{It is not very relaxed. Currently everything is using a dicionary as memory model and stick with that. The abstract value for each expression is the one *really* unspecified.}

The next two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTI} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural-number arithmetic,
and further binds the generic abstract interpreter to perform constant propagation.
%
An alternative to \Lang would be to define \lsti{ImpGAI} as a functor parameterized
by the abstract domain and such. But it would prevent \lsti{ImpCP} from reusing
the code and proofs in \lsti{ImpGAI}, because \lsti{ImpCP} involves extending
inductive types with new constructors.

>>>>

A second family \lsti{ImpGAI} (\textasciitilde 550~LOC) extends \lsti{Imp}.
It exports a generic framework for deriving
abstract interpreters with partial-correctness guarantees.
Soundness of the abstract interpreter, \lsti{analyze},
is stated with respect to the interpreter, \lsti{eval}, inherited from \lsti{Imp}.
The theorem says that the concretization relation \lsti{RState} over a
concrete state~\lsti{S} and an abstract state~\lsti{absS} is preserved
by the analysis:

@@

\noindent
\lsti{analyze} is defined via \lsti{FRecursion}, and the soundness theorem
is proved via \lsti{FInduction}.
This family leaves fields representing the abstract domain, the
concretization relation, monotonicity of transfer functions, etc.\ 
largely unspecified or unproven---a derived family can further bind
these ``parameters'' by overriding appropriate fields (and also possibly
extend the abstract syntax), to create a sound, runnable abstract
interpreter for a (possibly extended) while-language.
%\EDJ{It is not very relaxed. Currently everything is using a dicionary as memory model and stick with that. The abstract value for each expression is the one *really* unspecified.}

The next two families then extend \lsti{ImpGAI}.
Family \lsti{ImpTI} (\textasciitilde200~LOC) is an abstract
interpreter that does type inference~\cite{cousot1997types}.
Family \lsti{ImpCP} (\textasciitilde300~LOC) extends the abstract syntax
with natural-number arithmetic,
and further binds the generic abstract interpreter to perform constant propagation.
%
%An alternative to \Lang would be to define \lsti{ImpGAI} as a functor parameterized
%by the abstract domain and such. But it would prevent \lsti{ImpCP} from reusing
%the code and proofs in \lsti{ImpGAI}, because \lsti{ImpCP} involves extending
%inductive types with new constructors.
